Title

### 2013-02-25 inc/extension/liouvilles_theorem/liouvilles_theorem.tex
tweak liouvilles_theorem section

To evaluate the effect of this theorem on these equations, consider the time derivative of the product $\sigma_{\alpha} \eta_{\alpha}$.
Using \ref{eq:ag_original} it is easy to show that
\begin{gather}
  \frac{d}{dt} (\sigma_{\alpha} \eta_{\alpha}) = \sigma_{\alpha} \frac{d \eta_{\alpha}}{dt} + \eta_{\alpha} \frac{d \sigma_{\alpha}}{dt} = 0\\
  \label{eq:define_big_gamma}
  \therefore \sigma_{\alpha} \eta_{\alpha} \equiv \Gamma_{\alpha}^2 = \text{Constant}
\end{gather}
This analysis shows that the Analytic Gaussian model explicitly obeys the Liouville Theorem.

>>>>

In the AG model this phase space product is simply $\sigma_{\alpha} \eta_{\alpha}$
To evaluate the effect of this theorem on these equations, consider the time derivative of this product
Using \ref{eq:ag_original} it is easy to show that
\begin{gather}
  \frac{d}{dt} (\sigma_{\alpha} \eta_{\alpha}) = \sigma_{\alpha} \frac{d \eta_{\alpha}}{dt} + \eta_{\alpha} \frac{d \sigma_{\alpha}}{dt} = 0\\
  \label{eq:define_big_gamma}
  \therefore \sigma_{\alpha} \eta_{\alpha} \equiv \Gamma_{\alpha}^2 = \text{Constant}
\end{gather}
showing that the Analytic Gaussian model explicitly obeys the Liouville Theorem.
